### 2016-06-27 Docs/makefiles/makefiles.tex

The microphysics, as described above is also included.  For the networks,
we include a file called {\tt NETWORK\_REQUIRES} into {\tt GMaestro.mak}
that tells us whether to also include {\tt Util/VODE} (if {\tt NEED\_VODE := t})
or {\tt Util/BLAS} (if {\tt NEED\_BLAS := t}).

>>>>

The microphysics, as described above is also included.  For the
networks, we include a file called {\tt NETWORK\_REQUIRES} into {\tt
  GMaestro.mak} that tells us whether to also include {\tt Util/VODE}
(if {\tt NEED\_VODE := t}).  It is assumed in this case that we need
BLAS and LINPACK, so these are compiled in from {\tt Util/BLAS}  and
{\tt Util/LINPACK}.

You can instead link in a system-wide optimized BLAS library by setting
{\tt SYSTEM\_BLAS := t}\otherindex{{\tt GNUmakefile}}{BLAS} in the {\tt GNUmakefile}.  This adds {\tt -lblas}
to the link line, and assumes that the library is in your path.  Note
that for some systems, you should have the static BLAS libraries 
available.
